### 2016-10-07 sections/math.tex
Update on Overleaf.

>>>>

\subsection{Error estimation}

(following taken from \cite{SairaBanu2015})

Compression ratio:
$$CR=\frac{m n}{r(m+n+1)}$$

Mean square error:
$$MSE=\frac{1}{m n} \sum_{i=0}^{m-1} \sum_{j=0}^{n-1} (O_{ij} - R_{ij})^{2}$$
where \textit{O} represents the original image and \textit{R} represents the
reconstructed image of dimension $m \times n$.

Rooted Mean Square Deviation:
$$RMSD=\sqrt{MSE}$$

Normalized Rooted Mean Square Deviation:
$$NRMSD=\frac{RMSD}{X_{max}-X_{min}}=\frac{\sqrt{MSE}}{X_{max}-X_{min}}$$

Peak signal to noise ratio [db]:
$$PSNR=10\log_{10}\frac{(X_{max}-X_{min})^{2}}{MSE}$$

$$PSNR=20\log_{10}\frac{X_{max}-X_{min}}{\sqrt{MSE}}=20\log_{10}\frac{1}{NRMSD}$$

$$PSNR=-20\log_{10}NRMSD$$

\subsection{Randomized SVD}

\subsection{Sparse matrix of details}
